Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
curves edit third idea of pf

By equation \ref{eqn:deg1-sat-ind} for $k \in \BN$,
\[
	h^0(X, \lfloor k \halfcan \rfloor) = h^0(X, \lfloor k \halfcan'
		\rfloor) + \left\lfloor k \frac{\alpha} {\beta} \right \rfloor,
\] 
so $S$ contains elements in degree $k \in \BN$ with each pole order in $\{1 \ldots, \lfloor k\frac{\alpha}{\beta}\rfloor\}$.  Thus, by dimension counting, $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).

@@

\sssec{Idea of proof:} The construction of the $y_{i,e_i}$ in Part (a) uses Riemann--Roch and condition ~\ref{custom:Ad-iii}. The inequality in Part (a) follows from the fact that $L$ is similar to $L'$, but with some of the $e_i$ incremented by $2$. Part (b) follows by noting that the generators in Part (a) form an independent set, as can be seen by noting that the sublattice spanned by $y_{i,e_i}$ and $y_{i, e_i'}$ has determinant $1$ for $i \in J$. To check part (c) we construct relations between the generators of $R_{\halfcan}$ over $R_{\halfcan'}$. We note that an element lies in $R_{\halfcan'}$ if and only if its pole order at $P_i$ for $i \in J$ is not too large, and use Lemma ~\ref{lem:admissible_inequality} to check this bound. Part (d) follows fairly easily from the definition of admissibility.

>>>>

By Equation ~\ref{eqn:deg1-sat-ind} for $k \in \BN$,
\[
	h^0(X, \lfloor k \halfcan \rfloor) = h^0(X, \lfloor k \halfcan'
		\rfloor) + \left\lfloor k \frac{\alpha} {\beta} \right \rfloor,
\] 
so $S$ contains elements in degree $k \in \BN$ with each pole order in $\{1 \ldots, \lfloor k\frac{\alpha}{\beta}\rfloor\}$.  Thus, by dimension counting, $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).

@@

\sssec*{Idea of proof:} The construction of the $y_{i, e_i}$ in Part (a) uses Riemann--Roch and condition ~\ref{custom:Ad-iii}. The inequality in Part (a) follows from the fact that $L$ is similar to $L'$, but with some of the $e_i$ incremented by $2$. Part (b) follows by noting that the generators in Part (a) form an independent set which can be seen by noting that the sub-lattice spanned by $y_{i,e_i}$ and $y_{i, e_i'}$ has determinant $1$ for $i \in J$. To check part (c), we construct relations between the generators of $R_{\halfcan}$ over $R_{\halfcan'}$: we note that an element lies in $R_{\halfcan'}$ if and only if its pole order at $P_i$ for $i \in J$ is not too large, and use Lemma ~\ref{lem:admissible_inequality} to bound pole orders. Part (d) follows fairly easily from the definition of admissibility.
